SAT Competition 2020\tnoteref{title}

### 2021-06-22 paper/main.tex
typos

The Incremental Library track was first introduced in SAT~Race~2015~\cite{Balyo:2015:SATRace} and also took place in SAT~Competitions 2016 and 2017.
In the Incremental Library track the underlying idea is to mimic scenarios
where a SAT solver is used as a back-end solver in a more complex tool
(typically solving a harder problem than SAT) and is called multiple times before 
the enclosing tool reaches its final state. 
``Incremental'' here refers to the idea that the individual calls to the SAT solver are not independent, but may share a common subset of the input clauses or differ in the presence of additional unit clause assumptions~\cite{Nadel:2014:Incremental,Fazekas:2019:IncrementalInprocessing}.\textcolor{red}{Should we not cite the 2004 temporal induction paper by Niklases here?}
Examples for applications of incremental SAT solving are counterexample-guided eastraction refinement (CEGAR) based approaches, e.g., for Bounded Model Checking~\cite{Strichman:2005:ARBMC}, SAT-based planning~\cite{Balyo:2017:IncrPlanning},
multi-agent path finding~\cite{DBLP:conf/ijcai/Surynek19}, and satisfiability modulo theories (SMT) solvers~\cite{Brummayer:2009:Boolector}.

@@

\paragraph{Description}
A short system description was required for each solver submission,
including a list of all  authors involved in developing the solver,  description of any non-standard algorithmic
techniques and data structures implemented in the sovler, as well as references to the relevant literature.
These system descriptions have been collected and made available publically in the non-refereed competition
proceedings~\cite{SC2020}.

@@

Variables which have to be assigned in all partial models of a formula as \emph{essential} (as opposed to \emph{don't care}-values)~\cite{Bryant:1987:Essentials}. 
The application \textsf{genipaessentials} incrementally determines essential variables in a given satisfiable formula~\cite{Balyo:2015:SATRace}. 
For this applicaiton, we used the same $50$  satisfiable instances as for  backbone computation.

@@

The clear winner of the Cloud track is \solver{Mallob-Mono} and the runner-up is \solver{TopoSAT2}
(see Figure~\ref{fig:res-cloud}).
\solver{Mallob-Mono} was able to solve more instances in 1000 seconds than the 
winner of the Parallel Track in 5000 seconds, which shows the potential of distributed SAT solving. 
The other four participants performed significantly worse. 
The massive parallelism in distributed SAT solving imposes additional challanges on scalable information sharing and search diversification. 
Since 2020 was the first year of this track, we expect a tighter competition in the future.

@@

\solver{Painless-MCOMSPS-STR} integrates the solver \solver{MapleCOMSPS} in the \solver{Painless} parallelization framework~\cite{Frioux:2017:Painless,Liang:2017:Maplecomsps}. 
The authors submitted a \solver{32} and a \solver{64} threaded variant, which alltogether won three awards, achieving
 the first place overall, the best score on satisfiable and the second-best score on unsatisfiable instances. 
The \solver{32} threaded variant achieved slightly better scores than the \solver{64} threaded variant overall
Furthermore, 
 the \solver{32} threaded variants geared towards either satisfiable or unsatisfiable instances 
showed much better  than the the \solver{64} threaded variants. \textcolor{red}{Not sure if I got this right: did the submit variants of the solver geared specifically towards SAT and UNSAT, resp.? The writing was really confusing here...}
% such that the runner-up solvers outperformed the \solver{64} threaded variant.

@@

In this section, we provide additional analysis of the Main track results, going beyond the rankings.
In paricular, we focus on metrics complementing the PAR-2 score used for ranking the solvers in the actual competition.

@@

The metric VBS-2 identifies \solver{Kissat-sat} as the best solver. Its leading score of \SI{32.9}{\percent} of the total
is somewhat more difficult to interpret, though: a solver can score \SI{32.9}{\percent} of VBS-2 total
by solving \SI{32.9}{\percent} of the solved instances in the best observed time
and no others. Howeer,  we see from its VBS-1 score that \solver{Kissat-sat} solved \SI{9.8}{\percent}
of the solved instances in the best observed time (and some others).
A solver can also score \SI{32.9}{\percent} of VBS-2 total by solving all the solved instances,
but always being roughly three times slower than the VBS. 
The performance of \solver{Kissat-sat} lies (obviously) somewhere between these two extremes.

@@

A greedy set cover of the solved instances by solvers of the Main track is presented in Table~\ref{tab:gscMain}. 
In the first iteration, the solver which solved the highest number of instances is selected; in our case it was \solver{Kissat-sat} with 264 instances as we know already from Table~\ref{tab:results}.
With these
 264 instances already covered, \solver{CaDiCaL-alluip} is the best in further contributing to the set by additional $22$ instances in iteration $2$.
We can see that the further iterations tend to add very little,
with the final four iterations adding one instance each. Note that each solver
that managed to solve an instance uniquely (i.e., being the only solver that solved a particular instance)
showis up in the greedy set cover. 
% for example the case of the last listed  
%\solver{exp-V-LGB-MLD-CBT-DL}.
Highlighting solvers that uniquely solve instance is a property of the greedy set cover metric
which we believe is congruent with documenting contributions to the state of the art.
\textcolor{red}{congruent...? maybe a better choice of words here?}

@@

Contributions to the VBS can becaptured by clustering the instance space into instance families. 
We evaluate the runtimes of the three winning solvers of the Main track on those new families which are represented by at least $14$ instances (cf.~Table~\ref{tab:families})
and report their place and score in Table~\ref{tab:eval-by-family}. 
Interestingly, the overall best solver \solver{Kissat-sat} is outperformed by the second and third ranked solvers \solver{Relaxed-newTech} and \solver{CMS-ccnr-lsids} on the \emph{Anti-Bandwidth}, \emph{Vlsat}, and \emph{Influence Maximization} families by a large margin.

@@

Interestingly, one identifiable large cluster consists of the \solver{Maple}-decedants, 
all of which are modifications of the winners in the SAT Competition 2018 and
the SAT Race 2019.
The similarity within the cluster is high, with the exception of
\solver{Scavel} and \solver{exp\_V\_MLD\_CBT\_DL}.
They form a sub-cluster
with a lower similarity compared to the rest, but a high similarity within. In fact, the highest measured similarity,
 % of $0.96$
besides the aforementioned \solver{CaDiCaL-alluip}, is observed between them.
The two solvers are both based on
\solver{MapleLCMDistChronoBT-dl-v2.2}, but have different authors.
This high similarity suggests that the
changes they made either result in a very similar behavior or do not have a
significant impact on the runtime performance.

@@

This year the Hack track was organized for hacks of \solver{Glucose 3}. 
In the next competition, we plan on moving to the well structured and documented state-of-the-art SAT solver \solver{CaDiCaL}. 
The \solver{CaDiCaL-alluip} solver---which is a modified \solver{CaDiCaL}---has shown competitive performance in this competitition.

The first instantiation of an Application track was the Planning track organized as a one-time track in 2020.. 
The results show that different solvers take the lead when we only evaluate for a single application, when compared to the overall Main track results.
We intend to run further instantiations of the Application track. 
While essentially none of the solvers that participated in the Planning track seemd particularly optimized for Planning instance, we hope
in future iterations the community will pick up on the challenge of optimizing SAT solvers towards different focus applications, as a complementary
challenge when compared to the generality of the Main track.
In the next competition, the  planned focus of Application track will be on SAT solver applications in cryptology.

>>>>

The Incremental Library track was first introduced in SAT~Race~2015~\cite{Balyo:2015:SATRace} and also took place in SAT~Competitions 2016 and 2017.
In the Incremental Library track the underlying idea is to mimic scenarios
where a SAT solver is used as a back-end solver in a more complex tool
(typically solving a harder problem than SAT) and is called multiple times before 
the enclosing tool reaches its final state. 
``Incremental'' here refers to the idea that the individual calls to the SAT solver are not independent, but may share a common subset of the input clauses or differ in the presence of additional unit clause assumptions~\cite{Nadel:2014:Incremental,Fazekas:2019:IncrementalInprocessing}.\textcolor{red}{Should we not cite the 2004 temporal induction paper by Niklases here?}
Examples for applications of incremental SAT solving are counterexample-guided abstraction refinement (CEGAR) based approaches, e.g., for Bounded Model Checking~\cite{Strichman:2005:ARBMC}, SAT-based planning~\cite{Balyo:2017:IncrPlanning},
multi-agent path finding~\cite{DBLP:conf/ijcai/Surynek19}, and satisfiability modulo theories (SMT) solvers~\cite{Brummayer:2009:Boolector}.

@@

\paragraph{Description}
A short system description was required for each solver submission,
including a list of all  authors involved in developing the solver,  description of any non-standard algorithmic
techniques and data structures implemented in the solver, as well as references to the relevant literature.
These system descriptions have been collected and made available publicly in the non-refereed competition
proceedings~\cite{SC2020}.

@@

Variables which have to be assigned in all partial models of a formula as \emph{essential} (as opposed to \emph{don't care}-values)~\cite{Bryant:1987:Essentials}. 
The application \textsf{genipaessentials} incrementally determines essential variables in a given satisfiable formula~\cite{Balyo:2015:SATRace}. 
For this application, we used the same $50$  satisfiable instances as for  backbone computation.

@@

The clear winner of the Cloud track is \solver{Mallob-Mono} and the runner-up is \solver{TopoSAT2}
(see Figure~\ref{fig:res-cloud}).
\solver{Mallob-Mono} was able to solve more instances in 1000 seconds than the 
winner of the Parallel Track in 5000 seconds, which shows the potential of distributed SAT solving. 
The other four participants performed significantly worse. 
The massive parallelism in distributed SAT solving imposes additional challenges on scalable information sharing and search diversification.
Since 2020 was the first year of this track, we expect a tighter competition in the future.

@@

\solver{Painless-MCOMSPS-STR} integrates the solver \solver{MapleCOMSPS} in the \solver{Painless} parallelization framework~\cite{Frioux:2017:Painless,Liang:2017:Maplecomsps}. 
The authors submitted a \solver{32} and a \solver{64} threaded variant, which altogether won three awards, achieving
 the first place overall, the best score on satisfiable and the second-best score on unsatisfiable instances. 
The \solver{32} threaded variant achieved slightly better scores than the \solver{64} threaded variant overall
Furthermore, 
 the \solver{32} threaded variants geared towards either satisfiable or unsatisfiable instances 
showed much better  than the the \solver{64} threaded variants. \textcolor{red}{Not sure if I got this right: did the submit variants of the solver geared specifically towards SAT and UNSAT, resp.? The writing was really confusing here...}
% such that the runner-up solvers outperformed the \solver{64} threaded variant.

@@

In this section, we provide additional analysis of the Main track results, going beyond the rankings.
In particular, we focus on metrics complementing the PAR-2 score used for ranking the solvers in the actual competition.

@@

The metric VBS-2 identifies \solver{Kissat-sat} as the best solver. Its leading score of \SI{32.9}{\percent} of the total
is somewhat more difficult to interpret, though: a solver can score \SI{32.9}{\percent} of VBS-2 total
by solving \SI{32.9}{\percent} of the solved instances in the best observed time
and no others. However, we see from its VBS-1 score that \solver{Kissat-sat} solved \SI{9.8}{\percent}
of the solved instances in the best observed time (and some others).
A solver can also score \SI{32.9}{\percent} of VBS-2 total by solving all the solved instances,
but always being roughly three times slower than the VBS. 
The performance of \solver{Kissat-sat} lies (obviously) somewhere between these two extremes.

@@

A greedy set cover of the solved instances by solvers of the Main track is presented in Table~\ref{tab:gscMain}. 
In the first iteration, the solver which solved the highest number of instances is selected; in our case it was \solver{Kissat-sat} with 264 instances as we know already from Table~\ref{tab:results}.
With these
 264 instances already covered, \solver{CaDiCaL-alluip} is the best in further contributing to the set by additional $22$ instances in iteration $2$.
We can see that the further iterations tend to add very little,
with the final four iterations adding one instance each. Note that each solver
that managed to solve an instance uniquely (i.e., being the only solver that solved a particular instance)
shows up in the greedy set cover.
% for example the case of the last listed  
%\solver{exp-V-LGB-MLD-CBT-DL}.
Highlighting solvers that uniquely solve instance is a property of the greedy set cover metric
which we believe is congruent with documenting contributions to the state of the art.
\textcolor{red}{congruent...? maybe a better choice of words here?}

@@

Contributions to the VBS can be captured by clustering the instance space into instance families.
We evaluate the runtimes of the three winning solvers of the Main track on those new families which are represented by at least $14$ instances (cf.~Table~\ref{tab:families})
and report their place and score in Table~\ref{tab:eval-by-family}. 
Interestingly, the overall best solver \solver{Kissat-sat} is outperformed by the second and third ranked solvers \solver{Relaxed-newTech} and \solver{CMS-ccnr-lsids} on the \emph{Anti-Bandwidth}, \emph{Vlsat}, and \emph{Influence Maximization} families by a large margin.

@@

Interestingly, one identifiable large cluster consists of the \solver{Maple}-descendants,
all of which are modifications of the winners in the SAT Competition 2018 and
the SAT Race 2019.
The similarity within the cluster is high, with the exception of
\solver{Scavel} and \solver{exp\_V\_MLD\_CBT\_DL}.
They form a sub-cluster
with a lower similarity compared to the rest, but a high similarity within. In fact, the highest measured similarity,
 % of $0.96$
besides the aforementioned \solver{CaDiCaL-alluip}, is observed between them.
The two solvers are both based on
\solver{MapleLCMDistChronoBT-dl-v2.2}, but have different authors.
This high similarity suggests that the
changes they made either result in a very similar behavior or do not have a
significant impact on the runtime performance.

@@

This year the Hack track was organized for hacks of \solver{Glucose 3}. 
In the next competition, we plan on moving to the well structured and documented state-of-the-art SAT solver \solver{CaDiCaL}. 
The \solver{CaDiCaL-alluip} solver---which is a modified \solver{CaDiCaL}---has shown competitive performance in this competition.

The first instantiation of an Application track was the Planning track organized as a one-time track in 2020.. 
The results show that different solvers take the lead when we only evaluate for a single application, when compared to the overall Main track results.
We intend to run further instantiations of the Application track. 
While essentially none of the solvers that participated in the Planning track seemed particularly optimized for Planning instance, we hope
in future iterations the community will pick up on the challenge of optimizing SAT solvers towards different focus applications, as a complementary
challenge when compared to the generality of the Main track.
In the next competition, the  planned focus of Application track will be on SAT solver applications in cryptology.
